\section{Why \cp\ violation in the Kaon system is small}
 \label{sec:cpv_kaon}
 From the preceding chapter we understand why \cp\ violation in the
 Kaon system must be a small effect. Kaon decays involve, to first
 order, only two generations of quarks: $(u,d)$ and $(c,s)$. We just
 established that a $2\times 2$ mixing matrix does not contain \cp\
 violating terms. Now this is not the complete story, it is a bit more
 complicated: In the presence of three generations, we would have
 to revise our argument for the $2\times 2$ sub-matrix a little bit,
 after all now the $3\times 3$ matrix is unitary, so the unitarity
 constraints that we used in our complex-phase counting exercise
 don't apply to the $2\times 2$ sub-matrix anymore.

 But looking at the structure of the CKM matrix (Eq
 \ref{eq:ckmLambda}), we also see that the two first generations
 couple only very weakly to the third, in which case the $2\times 2$
 sub-matrix does in fact, to first order, represent a stand-alone
 $2\times 2$, unitary mixing matrix, without (meaningful) complex
 phases, and hence w/o \cp\ violation. In terms of the Wolfenstein
 parameterisations, it turns out that even up to $4th$ order in the
 small parameter $\lambda=0.22$, the top-left $2\times 2$ block is
 real.

 Therefore, \cp\ violation in the Kaon system could only be a higher
 order phenomenon, induced by the highly suppressed interaction of the
 first two generations with the third. We were probably very lucky to
 see it as early as we did. Because the mass of the neutral Kaon is very close the the
 mass of the three pions that the \cp-odd Kaon decays to, this decay is
 very much dis-favoured by phase-space - but very much favoured by the
 approximate \cp\ conservation. This phase-space suppression is the reason
 why the $K_L$ (``K-long'') lives so long. Relative to that, the decay
 to two pions is much favoured by phase space, which is why the $K_s$
 ``K-short'' lives so short relative to the $K_L$. Without this
 coincidence, where phase-space highly favours the 'forbidden' decay,
 we might never have seen the \cp\-violating decay of $K_L\to \pi\pi$ at
 all, or most likely much later.
